Face Attractiveness and the Sense of Reality

### 2024-09-02 analysis.Rmd

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggdist)
library(ggside)
library(easystats)
library(patchwork)
library(brms)

@@

@@

```{r make_models, message=FALSE, warning=FALSE, fig.width=fig.width, fig.height=fig.width, cache=cache}
rez_at <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Attractive, 2) + (1|Participant) + (1|Stimulus)",
  var = "Attractive", fill = "#F44336"
)
rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Beauty, 2) + Trustworthy + Familiar + (1|Participant) + (1|Stimulus)",
  var = "Beauty", fill = "#E91E63"
)
rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Trustworthy, 2) + Beauty + Familiar + (1|Participant) + (1|Stimulus)",
  var = "Trustworthy", fill = "#4CAF50"
)
rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Familiar, 2) + Beauty + Trustworthy + (1|Participant) + (1|Stimulus)",
  var = "Familiar", fill = "#2196F3"
)
```

>>>>

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggdist)
library(ggside)
library(easystats)
library(patchwork)
library(brms)
library(psych) # reliability analysis

set.seed(33)

@@

## Scales - Reliability analysis {.tabset}

### IPIP

```{r}
#extraversion
dplyr::select(df, starts_with("Extraversion_")) |>
psych::alpha(check.keys = TRUE) # 0.82

#Conscientiousness
dplyr::select(df, starts_with("Conscientiousness_")) |>
psych::alpha(check.keys = TRUE) # 0.73

#Neuroticism 
dplyr::select(df, starts_with("Neuroticism_")) |>
psych::alpha(check.keys = TRUE) # 0.59

#Openness
dplyr::select(df, starts_with("Conscientiousness_")) |>
psych::alpha(check.keys = TRUE) # 0.73

#Honest-Humility
dplyr::select(df, starts_with("HonestyHumility_")) |>
psych::alpha(check.keys = TRUE) # 0.7

#Agreableness 
dplyr::select(df, starts_with("Agreeableness_")) |>
psych::alpha(check.keys = TRUE) # 0.82

```

### SIAS-6 and SPS-6

```{r}
#SIAS- social interaction scale
dplyr::select(df, starts_with("SIAS_")) |>
psych::alpha(check.keys = TRUE) # 0.84

#SPS - social phobia scale
dplyr::select(df, starts_with("Social_Phobia_")) |>
psych::alpha(check.keys = TRUE) # 0.87

```

### Expectations about AI technology and GAAIS

<!-- Expectations about AI = items that did not said OG scale item from the parameters.js (GAAIS_1;3;5;7;10) -->

```{r}

#expectations about AI
dplyr::select(df, AI_1_RealisticImages, AI_3_VideosReal, AI_5_ImitatingReality, AI_7_RealisticVideos, AI_10_FaceErrors) |>
psych::alpha(check.keys = TRUE) # 0.61

#GAAIS
dplyr::select(df, AI_2_Unethical, AI_4_DailyLife, AI_6_Dangerous, AI_8_Exciting, AI_9_Applications) |>
psych::alpha(check.keys = TRUE) # 0.74

## positive GAAIS
dplyr::select(df, AI_4_DailyLife, AI_8_Exciting, AI_9_Applications) |>
psych::alpha(check.keys = TRUE) # 0.74

## negtavive GAAIS
dplyr::select(df, AI_2_Unethical, AI_6_Dangerous) |>
psych::alpha(check.keys = TRUE) # 0.74

```

### FFNI-BF

#### Low-order dimensions

```{r}

#acclaim seeking 
dplyr::select(df, Acclaim_Seeking_1, Acclaim_Seeking_16) |>
psych::alpha(check.keys = TRUE) # 0.68

#authoritativeness
dplyr::select(df, Authoritativeness_3, Authoritativeness_18) |>
psych::alpha(check.keys = TRUE) # 0.77

#grandiose fantasies
dplyr::select(df, Grandiose_Fantasies_8, Grandiose_Fantasies_23) |>
psych::alpha(check.keys = TRUE) # 0.8

#Exhibition 
dplyr::select(df, Exhibitionism_6, Exhibitionism_21) |>
psych::alpha(check.keys = TRUE) # 0.65

#Manipulativeness
dplyr::select(df, Manipulativeness_11, Manipulativeness_26) |>
psych::alpha(check.keys = TRUE) # 0.58

#Exploitativeness
dplyr::select(df, Exploitativeness_7, Exploitativeness_22) |>
psych::alpha(check.keys = TRUE) # 0.74

# Entitlement 
dplyr::select(df, Entitlement_5, Entitlement_20) |>
psych::alpha(check.keys = TRUE) # 0.8

#  Lack of empathy
dplyr::select(df, Lack_of_Empathy_10, Lack_of_Empathy_25) |>
psych::alpha(check.keys = TRUE) # 0.68

#Arrogance 
dplyr::select(df, Arrogance_2, Arrogance_17) |>
psych::alpha(check.keys = TRUE) # 0.59

# Reactive Anger
dplyr::select(df, Reactive_Anger_13, Reactive_Anger_28) |>
psych::alpha(check.keys = TRUE) # 0.66

# Distrut
dplyr::select(df, Distrust_19, Distrust_4) |>
psych::alpha(check.keys = TRUE) # 0.55

# Thrill Seeking 
dplyr::select(df, Thrill_Seeking_15, Thrill_Seeking_30) |>
psych::alpha(check.keys = TRUE) # 0.77

# Shame
dplyr::select(df, Shame_14, Shame_29) |>
psych::alpha(check.keys = TRUE) # 0.72

# Indifference 
dplyr::select(df, Indifference_9, Indifference_24) |>
psych::alpha(check.keys = TRUE) # 0.63

# Need for admiration
dplyr::select(df, Need_for_Admiration_12, Need_for_Admiration_27) |>
psych::alpha(check.keys = TRUE) # 0.57

```

#### High-order dimensions

```{r}

##agentic narcissism

dplyr::select(df, Acclaim_Seeking_1, Acclaim_Seeking_16, Authoritativeness_3, Authoritativeness_18, Grandiose_Fantasies_8, Grandiose_Fantasies_23,  Exhibitionism_6, Exhibitionism_21) |>
psych::alpha(check.keys = TRUE) #0.78

#Antognistic Narcissism

dplyr::select(df, Manipulativeness_11, Manipulativeness_26, Exploitativeness_7, Exploitativeness_22, Entitlement_5, Entitlement_20, Lack_of_Empathy_10, Lack_of_Empathy_25, Arrogance_2, Arrogance_17, Reactive_Anger_13, Reactive_Anger_28, Distrust_19, Distrust_4, Thrill_Seeking_15, Thrill_Seeking_30) |>
psych::alpha(check.keys = TRUE) # 0.83

# Neurotic Narcissism

dplyr::select(df, Shame_14, Shame_29, Indifference_9, Indifference_24, Need_for_Admiration_12, Need_for_Admiration_27) |>
psych::alpha(check.keys = TRUE) # 0.79

```

### R-GPTS

```{r}
# Reference
dplyr::select(df, starts_with("Reference_")) |>
psych::alpha(check.keys = TRUE) # 0.85

#Prosecution 
dplyr::select(df, starts_with("Persecution_")) |>
psych::alpha(check.keys = TRUE) # 0.93

```

### IUS-12

```{r}

# Prospective anxiety 
dplyr::select(df, starts_with("Prospective_Anxiety_")) |>
psych::alpha(check.keys = TRUE) # 0.8

#Inhibitory anxiety
dplyr::select(df, starts_with("Inhibitory_Anxiety_")) |>
psych::alpha(check.keys = TRUE) # 0.82

```

### Sel-rated attractiveness

```{r}

dplyr::select(df, self_rated_general_attractiveness, self_rated_physical_attractiveness) |>
psych::alpha(check.keys = TRUE) # 0.94

```

:::

@@

```{r make_models, fig.height=fig.width, fig.width=fig.width, message=FALSE, warning=FALSE, cache=FALSE}
rez_at <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Attractive, 2) + (1|Participant) + (1|Stimulus)",
  var = "Attractive", fill = "#F44336"
)
rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Beauty, 2) + Trustworthy + Familiar + (1|Participant) + (1|Stimulus)",
  var = "Beauty", fill = "#E91E63"
)
rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Trustworthy, 2) + Beauty + Familiar + (1|Participant) + (1|Stimulus)",
  var = "Trustworthy", fill = "#4CAF50"
)
rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Familiar, 2) + Beauty + Trustworthy + (1|Participant) + (1|Stimulus)",
  var = "Familiar", fill = "#2196F3"
)
```
